Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-11-01 Arxiv/main.tex
Update Arxiv/main.tex

\subsubsection{Dilation Property of $\hexpmech$}
\begin{lem}
\label{lem_dilation}
Given $\hexpmech(\dataobs)$ in Beta-binomial system, for any $r\in \candidateset$, let $\lambda < |\gamma|$, $\epsilon$, $|\delta'| < 1$ and $\gamma \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the following \emph{dilation property} holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}} + \frac{\delta'}{2}.
\end{equation*}
\end{lem}

@@

          Particularly, $|\candidateset| = n + 1$ because in Beta-binomial system.

@@

\subsubsection{$\hexpmech$ $2\epsilon$ Privacy Analysis}

>>>>

\subsubsection{Dilation Property of $\hexpmech$}
\begin{lem}
\label{lem_dilation}
Given $\hexpmech(\dataobs)$ in Beta-binomial system, for any $r\in \candidateset$, let $1 - \frac{\delta'}{2} = |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})$, the following \emph{dilation property} holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}} + \frac{\delta'}{2}.
\end{equation*}
\end{lem}

@@

          Particularly, $|\candidateset| = n + 1$ in Beta-binomial system.

@@

\subsubsection{$\hexpmech$ $2\epsilon-$Differential Privacy Proof}
